---
title: "04-gam-cc-obs-gridded.Rmd"
author: "Whitney Friedman"
date: '2022-05-17'
output: html_document
---
# Random Forest Model of observed coral cover
- % coral cover data from global surveys, aligned with 5km LRP cells
- environmental co-variates aggregated to 5km LRP cells

# Setup
```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
```

## load libraries & functions
```{r message=FALSE, warning=FALSE, include=TRUE}
library(here)
source(here("00-load-cc-libraries.R"))
library(corrplot)
library(arm)
library(optimx)
library(mgcv)
library(mgcViz) # better GAM visualizations
library(ranger)
library(randomForest)
library(sf)
library(RColorBrewer)
conflict_prefer("view", "tibble")
library(skimr)
library(janitor)
library(kableExtra)


# Load functions
source(here( "00-load-cc-functions.R"))
```

## ALT: load workspace
```{r eval = F}
load(here("outputs","04a-gcc-v1-4-model.Rdata"))
```

## load data
```{r}
# observed coral cover
cc_dat <- read_rds(here("data", "allreefs_coralcover.RDS")) %>% 
  as_tibble() %>% 
  select(OBJECTID, geometry, pct_hardcoral:method_cat)

# environmental and social variables
# remove - redundant with below
# env_dat <- read_rds(here("data", "allreefs_gcc.RDS")) %>% 
#   rename(OBJECTID = objectid)

lrp_coords <- read_csv(here("data","allreefs_centroids.csv"), 
                       col_types = c("c","d","d"))

# GCC table
gcc_df <- read_rds(file = here("data", "allreefs_gcc.RDS"))

```

## prep data
Join tables; keep only cells with coral cover data
- For (10) LRP cells with 'unknown' survey method, set to 'pitlitbleach'
- these are all ETP; will fold in with region otherwise. Safe to assume since its from a long term DB
```{r}
lrp_gcc_df <- gcc_df %>% 
  mutate(pct_hardcoral_transform = beta_transform(pct_hardcoral),
         population_log = log1p(pop_count_raw),
         effluent_openN_log = log1p(effluent_open_n),
         effluent_totN_log = log1p(effluent_total_n),
         dist_from_eq = abs(0-latitude)) %>% 
  mutate(mgmt_highest = if_else(mgmt_highest == "unknown", "open access", mgmt_highest), 
         mgmt_highest = factor(mgmt_highest, 
                               levels = c("open access", "restricted", "no take"), 
                               ordered = F)) %>% 
  select(-c(sample_yr_min, sample_yr_max, grav_nc_raw))

lrp_gcc_df %>% select(-geometry) %>% skim() # nrows = 54596

lrp_gcc_df %>% tabyl(mgmt_highest)
lrp_gcc_df %>% tabyl(method_cat)

# 1671 model cells
ccmod_df <- lrp_gcc_df %>% 
  filter(!is.na(pct_hardcoral))

ccmod_df %>% select(-geometry) %>% skim()
ccmod_df %>% tabyl(region)
ccmod_df %>% tabyl(country)      # not enough samples per country; use region
ccmod_df %>% tabyl(mgmt_highest)

ccmod_df %>% 
  ggplot(aes(x = pct_hardcoral_transform))+
  geom_histogram()+
  facet_wrap(~method_cat)

ggsave(here("plots","SM_plots",
            "pct_hardcoral_by_method.png"), width = 7, height = 3)

```

# SAVE THESE TABLES
```{r}
# Save ----
lrp_gcc_df %>% 
  write_rds(here("outputs",
             "04a_lrp_gcc_df.RDS"))

lrp_gcc_sf <- lrp_gcc_df %>% 
  st_as_sf(crs=4326)

lrp_gcc_sf %>% 
  write_rds(here("outputs",
             "04a_lrp_gcc_sf.RDS"))

ccmod_df %>% 
  write_rds(here("outputs",
             "04a_ccmod_df.RDS"))

ccmod_sf <- ccmod_df %>% 
  st_as_sf(crs=4326)
  
# geojson
fn = here("outputs", "04a_ccmod_df.geojson")

if(file.exists(fn)){
  file.remove(fn)
}

st_write(ccmod_sf, dsn = fn, driver = "GeoJSON", append = F)


```


# Model Prep

## Correlations - all numeric predictors
- Using spearman (rank); if all are numeric could use pearson 
```{r}

png(here("plots", "SM_plots",
         "gcc_v1_4_correlations.png"), height = 12, width = 12, units = "in", 
    res = 300)

ccmod_df %>% 
  select(-c(objectid, geometry, country_iso, eez, starts_with("pct_hardcoral"))) %>% 
  mutate_if(is.factor, as.numeric) %>% 
  select_if(is.numeric) %>% 
  cor(use = "pairwise.complete.obs", method = "spearman") %>% 
  corrplot::corrplot(method = "color", addCoef.col = 'black', diag = F, 
                     tl.cex = .5, tl.col = "black",
                     number.cex = 0.5)

dev.off()

# SST correlations
png(here("plots",
         "gcc_v1_4_correlations_sst.png"), height = 7, width = 7, units = "in", 
    res = 300)

ccmod_df %>% 
  select(starts_with("sst"), 
         contains("dhw")) %>% 
  cor(use = "pairwise.complete.obs", method = "pearson") %>% 
  corrplot::corrplot(method = "color", addCoef.col = 'black', diag = F, 
                     order = "hclust",
                     tl.cex = .7, tl.col = "black",
                     number.cex = 0.7, 
                     cl.cex = 0.7)

dev.off()
```

## ALT: load RF and XGB
```{r eval = F}
rf_final <- read_rds(here("outputs",
                "gcc_v1_4_random_forest.RDS"))

ccmod_xgb <- read_rds(here("outputs",
                "gcc_v1_4_xgb.RDS"))
```


## Random forest
Use random forest to get variable importance and maximal performance
R Packages 'caret' and 'randomForest'
Then switch to GAM (for generalization)

```{r}
# General Setup
set.seed(1986) # All models are random, want this to be reproducible. Delete this to see effect of randomness.

Sys.getenv('R_MAX_VSIZE')
Sys.setenv('R_MAX_VSIZE'='10.0Gb') # set under limit of physical memory

# all variables (n = 40)
rf_allvars <- c("latitude", "longitude","dist_from_eq",
         "pop_count_raw", "num_ports_raw", "reef_value_raw", 
         "sediment_raw", "nutrient_raw", "score_cy", "score_cn",
         "dhw0", "dhw4", "dhw_max_cumul",
         "sst_range", "sst_var", "sst_max", #  supplied from CRW
         # UNCOMMENT TO USE: these variables are only ~80% complete (~300 missing) 
         # "npp_mean" ,"npp_sd","reef_area_15km", "wave_energy_mean",      
         "effluent_totN_log", "effluent_openN_log", 
         "calcite", "dissolved_oxygen",
         "ph_mean", "par_max", "diffuse_atn_max", "currents_velocity_mean",
         "sst_skewness", "sst_kurtosis", "sst_annualtrend", 
         "sst_max", "sst_range", "sst_var",
         "aca_top_geo_simple", "aca_pr_lagoon", "aca_pr_slope", "aca_pr_crest",
         "aca_pr_bank","aca_pr_seagrass", "gebco_depth", "gs_vr_score", 
         "mgmt_highest", "method_cat", "region") %>% unique()

ccmod_rf_set <- ccmod_df %>% 
  select(pct_hardcoral_transform, all_of(rf_allvars))

# 1671 obs, 40 variables.
ccmod_rf_set %>% skim()
# ---- 

# cross val test for mtry value (mtry = 7)
library(caret)

nvars <- length(rf_allvars)
sqrt(nvars) # 6.1

rf_trControl = trainControl(
   method = "repeatedcv",
   number = 10,
   repeats = 3,
   savePredictions = "final"       # save predictions for the optimal tuning parameter
)

# run rf with caret (~10min)
ccmod_rf <- train(
   pct_hardcoral_transform ~ .,
   data = ccmod_rf_set,
   method = "rf",
   na.action = na.roughfix, # uses the median/mode to fill in missing data
   ntree = 2000,
   metric = "RMSE",
   tuneGrid = expand.grid(mtry = 5:8), # searching around mtry = sqrt(n_vars) (5:8)
   trControl = rf_trControl
)
beepr::beep() # beep when finished 

ccmod_rf
rf_final <- ccmod_rf$finalModel

write_rds(rf_final,
          here("outputs",
                "gcc_v1_4_random_forest.RDS"))

```

```{r}
print(rf_final) # var expl = 49.4 
plot(rf_final)
varImpPlot(rf_final)

rf_varimp <- randomForest::importance(rf_final) %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  mutate(keep = if_else(IncNodePurity > 1, 1,0)) %>% 
  arrange(-IncNodePurity)

p1_rf <- rf_varimp %>% 
  ggplot(aes(y = reorder(variable,IncNodePurity), x = IncNodePurity, fill = factor(keep)))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = c("grey60","black"), name = "Keep variable?", labels = c("no", "yes"))+
  ylab("")+xlab("Variable importance with random forest")+
  theme_minimal()

p1_rf

top_vars <- rf_varimp$variable[1:22]
top_vars <- top_vars[!top_vars %in%
                       c("method_catphoto","mgmt_highestunknown",
                         "regionCaribbean-Atlantic","method_catpitlitbleach")]
top_vars <- c(top_vars, c("method_cat", "mgmt_highest", "region"))

top_vars
```


## Boosted regresssion trees
ALTERNATIVE TO random forests
Possibly deals better with correlations

```{r}
library(xgboost)
library(caret)
set.seed(1986)

xgb_trControl = trainControl(
   method = "repeatedcv",
   number = 10,
   repeats = 3,
   savePredictions = "final"       # save predictions for the optimal tuning parameter
)

garbage <- capture.output(
ccmod_xgb <- train(
   pct_hardcoral_transform ~ .,
   data = ccmod_rf_set,
   na.action = na.roughfix, # uses the median/mode to fill in missing data
   method = "xgbTree",
   metric = "RMSE",
   tuneLength = 5,
   trControl = xgb_trControl
))

# beep when finished 
beepr::beep() 

# save 
write_rds(ccmod_xgb,
          here("outputs",
                "gcc_v1_4_xgb.RDS"))

```

```{r}
ccmod_xgb
ccmod_xgb$finalModel

varimp_xgb <- caret::varImp(ccmod_xgb)$importance %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "variable") %>% 
  rename(Importance = Overall) %>% 
  mutate(keep = if_else(Importance > 25, 1, 0))

p2_xgb <- varimp_xgb %>% 
  ggplot(aes(y = reorder(variable,Importance), x = Importance, fill = factor(keep)))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = c("grey60","black"), name = "Keep variable?", labels = c("no", "yes"))+
  ylab("")+xlab("Variable importance with XGBoost")+
  theme_minimal()

p2_xgb

```

## Compare RF and XGB
```{r}
# Compare RF and XGB
png(here("plots", "variable_importance.png"), 
    height = 6, width = 9, units = "in", res = 300)

ggpubr::ggarrange(p1_rf  + theme(text = element_text(size = 9)),
                  p2_xgb + theme(text = element_text(size = 9)),
                  nrow = 1, common.legend = T, legend = "bottom", 
                  labels = "AUTO")

dev.off()

# ALL top vars (RF and XGB)

top_vars_all <- c(rf_varimp$variable[rf_varimp$keep == 1], 
                  varimp_xgb$variable[varimp_xgb$keep == 1]) %>% 
  unique()
  

top_vars_all <- top_vars_all[!top_vars_all %in%
                       c("method_catphoto","mgmt_highestunknown",
                         "regionCaribbean-Atlantic","method_catpitlitbleach")]
top_vars_all <- c(sort(top_vars_all), c("method_cat", "mgmt_highest", "region")) %>% 
  unique()

top_vars_all

# correlations among top vars (n=20)
# sst_kurtosis, sst_range
# sst_kurtosis, dist_from_eq

png(here("plots", "SM_plots",
         "gcc_v1_4_correlations_top_vars.png"), height = 7, width = 7, units = "in", 
    res = 300)

ccmod_df %>% 
  select(all_of(top_vars_all),-c(method_cat, mgmt_highest, region), latitude, longitude) %>% 
  mutate(across(everything(), ~(as.numeric(.)))) %>% 
  cor(use = "pairwise.complete.obs", method = "pearson") %>% 
  corrplot::corrplot(method = "color", addCoef.col = 'black', diag = F, 
                     order = "alphabet",
                     tl.cex = .6, tl.col = "black",
                     number.cex = 0.6)

dev.off()


```

# GAM Model Testing

## GAM Setup
- Consider variable transformations as appropriate

```{r}
#install_version("MuMIn", version = "1.46.0", repos = "http://cran.us.r-project.org")
library(MuMIn)
library(parallel)

# remove dist_from_eq; check population
gam_vars <- c(top_vars_all[!top_vars_all %in%
                         c("dist_from_eq","aca_pr_seagrass")]) %>% sort()

gam_vars %>% as_tibble() %>% 
  write_csv(here("intermediate-files","gam_vars.csv"))


# 1671 -> 1658!
gam_df <- ccmod_df %>% 
  select(pct_hardcoral_transform, all_of(gam_vars)) %>% 
  drop_na()

gam_df %>% skim()

```

## GAM Pre-checks
```{r}
# check variable distributions
for(v in c("pct_hardcoral_transform", gam_vars)){
  if(! v %in% c("method_cat","mgmt_highest","region", "latitude","longitude")){
    gam_df %>% pull(v) %>% hist(main = v)   
  }
}


corrs <- gam_df %>% 
  select(-c(pct_hardcoral_transform, method_cat, mgmt_highest, region)) %>% 
  as.matrix() %>% 
  cor(use = "pairwise.complete.obs", method = "pearson") %>% 
  as.data.frame() %>% 
  rownames_to_column(var = "var1") %>% 
  pivot_longer(calcite:sst_var, names_to = "var2", values_to = "cor")

# sst_kurtosis, sst_range 
corrs %>% 
  filter(var1 != var2, 
         abs(cor) >= .7)

```


## Generate candidate models
NOTE: this takes awhile (days!) to run. Eval is set to false by default.
```{r eval = F}
source(here("01a-gcc-v1-4-candidate-models.R")
```

## Read and compare candidate models
```{r}
# this file includes models with 4-7 variables. 4 variables = base model (lat, lon, method, mgmt, region)
# dredge 1-4: 
gam_dredge4 <- read_csv(here(
                              "intermediate-files","gam_dredge_4.csv"))
gam_dredge5 <- read_csv(here(
                              "intermediate-files","gam_dredge_5.csv"))
gam_dredge6 <- read_csv(here(
                              "intermediate-files","gam_dredge_6.csv"))
gam_dredge7 <- read_csv(here(
                              "intermediate-files","gam_dredge_7.csv"))
gam_dredge8 <- read_csv(here(
                              "intermediate-files","gam_dredge_8.csv"))
gam_dredge9 <- read_csv(here(
                              "intermediate-files","gam_dredge_9.csv"))

gam_dredge_combn <- rbind(gam_dredge4, gam_dredge5, gam_dredge6, gam_dredge7,
                          gam_dredge8, gam_dredge9)

lowest_aic <- min(gam_dredge_combn$AICc)

# 6415 candidate models
gam_dredge_df <- gam_dredge_combn %>% 
  clean_names() %>% 
  rename("aic_c" ="ai_cc") %>% 
  mutate(delta = aic_c - lowest_aic) %>%  
  mutate(across(matches("s_"), ~ ifelse(.=="+", 1, .))) %>%
  mutate(across(matches("mgmt_"), ~ ifelse(.=="+", 1, .))) %>% 
  mutate(across(starts_with("te_"), ~ ifelse(.=="+", 1, .))) %>% 
  mutate(n_terms = rowSums(across(starts_with("s_")), na.rm=T) + 2) %>% 
  distinct(pick(starts_with("s_")), .keep_all = T) %>% 
  rename_all(~str_replace(.,"s_","")) %>%
  rename_all(~str_replace_all(.,"_k_6_bs_cr|_bs_re|_bs_fs_k_6|_bgp_k_c_10_10_m_2","")) %>%  
  select(-weight) %>% 
  arrange(aic_c)

```

## Summarise
```{r}
# candidate model summary
gam_dredge_df %>% 
  select(n_terms, log_lik, dev_exp, aic_c) %>% 
  pivot_longer(-n_terms, names_to = "metric") %>% 
  ggplot(aes(x = factor(n_terms), y = value))+
  geom_boxplot()+
  facet_wrap(~metric, ncol = 3, scales = "free_y")

ggsave(here("plots","SM_Plots", 
          "candidate_model_summary.png"), height = 4, width = 9)

# candidate models with delta AICc < 4
gam_dredge_top <- gam_dredge_df %>% 
  arrange(aic_c) %>% 
  mutate(model = seq(1,nrow(gam_dredge_df))) %>% 
  relocate(model) %>% 
  filter(delta < 4)

gam_dredge_top


gam_dredge_top %>% write_csv(here("outputs","gam_dredge_top_models.csv"))

# variable names for the top model(s)
final_vars <- gam_dredge_top %>% 
  filter(model == 1) %>% 
  select_if(~ !all(is.na(.))) %>% 
  select(any_of(gam_vars)) %>% 
  names()

final_vars

# print for use in table 2
cat(c("te(lat,lon)",
    final_vars[!final_vars %in% c("mgmt_highest","method_cat","region")], 
    "mgmt_highest"),sep = " + ")

# table 2 (other cols)
gam_dredge_top %>% 
  select(model, n_terms, df, dev_exp, log_lik, aic_c, delta) %>% 
  kbl() %>% 
  kable_classic()

```


# Final GAM Models
```{r}
library(MuMIn)

# Final vars after model comparison:
# calcite + dhw_max_cumul + par_max + ph_mean + score_cn + sst_range + sst_skewness + mgmt_highest

final_vars %>% as_tibble() %>% 
  rename(variable = value) %>% 
    write_csv(here("outputs","gam_vars_final.csv"))
  
# 1671 --> 1663
gam1_df <- ccmod_df %>% 
  select(objectid, geometry, country,
         pct_hardcoral_transform,
         all_of(final_vars), latitude, longitude) %>% 
  drop_na()

gam1_df %>% select(-geometry) %>% skim()

# Check correlations (watch: par_max, sst_kurtosis; dissolved_oxygen, sst_max)
png(here("plots","SM_Plots", 
          "gam1_correlations.png"), height = 7, width = 7, units = "in", res = 300)
gam1_df %>% 
  select(all_of(final_vars)) %>% 
  mutate(across(everything(), ~as.numeric(.))) %>% 
  cor(use = "pairwise.complete.obs", method = "pearson") %>% 
  corrplot::corrplot(method = "color", addCoef.col = 'black', diag = F, 
                     tl.cex = 1, tl.col = "black",
                     number.cex = 1)
dev.off()

# VIF among top predictors
# Max VIF (adjusted) = 3.28 (longitude); all others < 2
DescTools::VIF(lm(pct_hardcoral_transform ~ ., 
                  data = gam1_df %>% select(pct_hardcoral_transform, 
                                            latitude, longitude,
                                            all_of(final_vars))))
```

## GAM 1 Generate model

Family: betar (proportions data on (0,1) when the binomial is not appropriate)
Link: The link function: one of "logit", "probit", "cloglog" and "cauchit".
theta: the extra parameter (phi above).
method: "REML", alts: "ML", "GCV" (REML is preferred b/c of stability)


```{r gam1}

final_vars
kmax = 6

# max performance for lat,lon with k = 14,14 (but time to generate each model increases A LOT)
# NOTE: computational limitations meant we couldn't test all gam models with k = 14,14; most
# were tested with k = 10,10
gam1 <- gam(pct_hardcoral_transform ~ 
              te(longitude,latitude, bs = "gp", k = c(14,14), m = 2) + 
              s(dhw_max_cumul, k=kmax, bs = "cr")+               # CHECK
              s(par_max, k=kmax, bs = "cr")+                    # m1
              s(ph_mean, k=kmax, bs = "cr") +                   # m1
              s(score_cn, k=kmax, bs = "cr") +                  # m1
              s(sst_skewness, k=kmax, bs = "cr")+               # m1
              mgmt_highest +                                    # all models
              s(method_cat, bs = 're') +                        # all models
              s(region, bs = 're'),                             # all models
            data = gam1_df, 
            gamr = 1.4, # higher penalty for complexity (default is 1)
            family = "betar", 
            link = "logit",# 
            method = "REML",
            na.action = "na.fail") 

# beep when the model is done
beepr::beep()

gam1_info <- tibble(
  model = "gam1",
  r_sq = summary(gam1)$r.sq, 
  edf = sum(influence(gam1)),
  dev_expl = summary(gam1)$dev.expl*100,
  logLik = logLik.gam(gam1)[1], 
  AICc = AICc(gam1))


gam1_info # max dev expl. (observed range = 53.5 - 55.77; current: 54.43)

```
```{r}
# Save as 'final'
gam_final <- gam1
gam_final_df <- gam1_df %>% 
  mutate(pct_hardcoral_predicted = gam_final$fitted.values)

## Save final model! 
write_rds(gam_final, here("outputs","gcc_v1_4_gam.RDS"))
write_rds(gam_final_df, here("outputs","gcc_v1_4_gam_df.RDS"))

```


## ALT: Load final model
```{r eval = False}

# load final gam model and info
gam_final <- read_rds(here("outputs","gcc_v1_4_gam.RDS"))

gam_final_df <- read_rds(here("outputs","gcc_v1_4_gam_df.RDS"))

```

## GAM 1 Performance

```{r}

# Observed vs. predicted - histogram

op_hist <- gam_final_df %>% 
  ggplot(aes(x =pct_hardcoral_transform))+
  geom_histogram(alpha = 0.6, fill = "gray10")+
  geom_histogram(aes(x = pct_hardcoral_predicted), 
                 alpha = 0.6, fill = "blue")+
  xlab("percent live hard coral")

op_hist

# Observed vs. predicted - 1:1 plot

op_line <- gam_final_df %>%
  ggplot(aes(y = pct_hardcoral_transform, x = pct_hardcoral_predicted))+
  geom_point(aes(colour = region), alpha = 0.8, size = 1, pch = 16)+
  scale_colour_manual(values = region_palette)+
  geom_smooth(method = lm, se = F, colour = "grey30", lwd = 0.5)+
  xlim(0,0.8)+ylim(0,0.8)+
  theme_light()+
  xlab("percent live hard coral: predicted")+
  ylab("percent live hard coral: observed")

op_line

png(here("plots","SM_Plots", 
          "gam1_obs_vs_pred.png"), height = 4, width = 9, units = "in", res = 300)

ggpubr::ggarrange(op_hist  + theme(text = element_text(size = 8)),
                  op_line + theme(text = element_text(size = 8)),
                  nrow = 1, common.legend = F,
                  labels = "AUTO", widths = c(1,1.5))

dev.off()


```

## GAM 1 Performace Cont'd
```{r}
# Model performance ----
summary(gam_final) # 54.4
# gam.check() plots: 
# q-q plot: should follow a 1:1 line
# histogram of residuals: should be approximately normal
# residuals vs. linear predictor: should be 
# observed vs. fitted values: 


# rep = 500, simulating data from response; creating confidence intervals on q-q plot
# Check k-index, should be > 1. k-index < 1 indicates additional variability 
# in the parameter that is not captured by the model.

gam.check(gam_final, rep = 500) 

# Correlation between raw and predicted values (r = 0.648)
cor(gam_final$y, gam_final$fitted.values, method = "pearson") # 0.674

# Takes a fitted gam object produced by gam() and plots the component smooth functions that make it up, on the scale of the linear predictor. Optionally produces term plots for parametric model components as well

plot(gam_final)
vis.gam(gam_final, theta = 10)
b <- getViz(gam_final)
print(plot(b, allTerms = T)) # Calls print.plotGam() pages = 1

png(here("plots", "SM_plots", "gam1_component_plot.png"), width = 12, height = 7, units = "in", res = 300)

print(plot(b, allTerms = T), pages =1) 

dev.off()
```


## GAM 0: Intercept Model
```{r gam0}
gam0 <- gam(pct_hardcoral_transform ~ 
              s(method_cat, bs = 're') +             # all models         
              s(region, bs = 're'),                  # all models         
            data = gam1_df, 
            family = "betar", 
            link = "logit",
            method = "REML", 
            na.action = "na.fail") 

gam0_info <- tibble(
  model = "gam0",
  r_sq = summary(gam0)$r.sq, 
  edf = sum(influence(gam0)),
  dev_expl = summary(gam0)$dev.expl*100,
  logLik = logLik.gam(gam0)[1], 
  AICc = AICc(gam0))

gam0_info
```

 
## Other figures
```{r}
# Partial plots ----
# THESE ARE NOT THE SAME AS THE MODEL -- geom_smooth provides a new (and different) fit. 
# TO USE this, need to EXTRACT from the actual model and re-plot using ggplot
# NOT NECESSARY ATM -- all this is included in SM

# visreg::visreg(gam_final,  gg=T, overlay = T, rug = T)

```


```{r}
# SEE COMMENT ABOVE
# ggplot(smooths, aes(x.val, value)) + 
#   geom_line() + 
#   geom_line(aes(y=value + 2*se), linetype="dashed") + 
#   geom_line(aes(y=value - 2*se), linetype="dashed") + 
#   facet_grid(. ~ x.var)
# 
# 
# draw(gam_final, residuals = TRUE)
# 
# # dhw_max_cumul + diffuse_atn_max + par_max + ph_mean + score_cn + sst_skewness + mgmt_highest
# gam_final_df %>% 
#   ggplot(aes(x = dhw_max_cumul, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = diffuse_atn_max, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = par_max, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = ph_mean, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = score_cn, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = sst_skewness, y = pct_hardcoral_predicted))+
#   geom_smooth()+
#   geom_rug(sides = "b")+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = region, y = pct_hardcoral_predicted))+
#   geom_boxplot()+
#   theme_light()
# 
# gam_final_df %>% 
#   ggplot(aes(x = method_cat, y = pct_hardcoral_predicted))+
#   geom_boxplot()+
#   theme_light()
# 
# # NOTE: most "unknown" cells have lower predicted (and observed) coral cover. 
# # :. if we test the counterfactual against mgmt_unknown cells, coral cover will always be higher
# # :. can only show difference where mgmt is currently KNOWN.
# # 
# # Open access ... "open access identified" vs. unknown = "open access presumed"
# # Unk is not likely to be no-take or restricted ... 
# # When management is happening, we know about it (restricted, no-take)
# # We're going to believe that "open access" is truly open access
# # AND when we don't know what it is, it's reasonable to presume that it's open access.
# 
# gam_final_df %>% 
#   ggplot(aes(x = mgmt_highest, y = pct_hardcoral_predicted))+
#   geom_boxplot()+
#   theme_light()
# 
```


# SAVE WORKSPACE ----
```{r eval=FALSE, include=FALSE}
# uncomment to save
# save.image(here("outputs","04a-gcc-v1-4-model.Rdata")) 

```

