---
title: "02-gcc-predict.Rmd"
author: "Whitney Friedman"
date: '2024-05'
output: html_document
---
# 02-gcc-predict.Rmd
Using the GAM model (gcc_v1.4) developed in 01-gcc-v1-4-model.Rmd
predict out to all local reef pressures ('lrp') coral reef cells, and
to a subset of coral reef monitoring sites.

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries & functions
```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
source(here("00-load-cc-libraries.R"))
library(mgcv)
library(sf)

# Load functions
source(here("00-load-cc-functions.R"))
```

## Load GCC data
```{r}
# load formatted data from 04a
lrp_gcc_df <- read_rds(here("outputs", "04a_lrp_gcc_df.RDS"))

lrp_gcc_df %>% select(-geometry) %>% skim()

lrp_gcc_sf <- read_rds(here("outputs", "04a_lrp_gcc_sf.RDS"))


```

## Load GAM model (gcc_v1.4)
```{r}
gcc_mdl <- read_rds(here("outputs","gcc_v1_4_gam.RDS"))

gcc_mdl_df <- read_rds(here("outputs","gcc_v1_4_gam_df.RDS"))

# read in final gam variables
gcc_vars <- read_csv(here("outputs","gam_vars_final.csv")) %>% 
  pull(variable)

gcc_vars

summary(gcc_mdl)
```

## Load site data, join to gcc
- Load site data
- For sites with multiple surveys, use most recent
- Spatial join with allreefs cells to get remaining data
```{r}
cc_dat <- read_rds(here("data","cc_surveys_combn.RDS")) %>% 
  rename(mgmt_highest = mgmt_simple) %>% 
  mutate(mgmt_highest = if_else(is.na(mgmt_highest), "open access", mgmt_highest), 
         mgmt_highest = factor(mgmt_highest)) %>% 
  # for sites with multiple surveys -- keep most recent
  arrange(-year) %>% 
  distinct(site, .keep_all = T) %>% 
  st_as_sf(coords = c("longitude","latitude"), remove = F,
           crs = 4326)

cc_dat %>% tabyl(mgmt_highest)

# join to GCC data 
cc_allreefs <- cc_dat %>% 
  st_join(lrp_gcc_sf %>% select(objectid, 
                                     all_of(gcc_vars), 
                                     -c(mgmt_highest, method_cat)), 
          join = st_intersects) %>% 
  select(-method)
  
cc_allreefs

# check all variables are present: 
gcc_vars %in% names(cc_allreefs)

```


# Predict CC globally (observed conditions)
Predict to global 5km reef cells using all known values

## Setup
set up table to use for prediction; variable formatting etc. must match model inputs
```{r}
predict_df <- lrp_gcc_df %>% 
  select(objectid, geometry, latitude, longitude, 
         region, country, method_cat,
         all_of(gcc_vars)) %>% 
  mutate(method_cat = if_else(is.na(method_cat), "pitlitbleach", method_cat), 
         method_cat = factor(method_cat))

# check for completeness & compare to gcc_mdl_df for variable types
predict_df %>% select(-geometry) %>% skim()
predict_df %>% tabyl(method_cat)
predict_df %>% tabyl(mgmt_highest)

gcc_mdl_df %>% select(-geometry) %>% skim()

```

## Predict for allreefs
Predict % live hard coral cover for all 5km grids with sufficient data 
(n = 54,298, or 99.45% of all global reef cells
Include standard error (SE) estimates
```{r}
# Baseline prediction
# Use the GCC model to predict coral cover in cells with no data
cc_pred <- predict.gam(gcc_mdl, type = "response", newdata=predict_df, se.fit = T)
cc <- cc_pred[[1]]
cc_se <- cc_pred[[2]]

# quartiles of predicted cc 
cc_pred_qt <- quantile(cc, na.rm=T)

# create new data fram of predictions
allreefs_cc <- predict_df %>% 
  bind_cols(pct_hardcoral_predicted = cc) %>% 
  bind_cols(pct_hardcoral_predicted_se = cc_se) %>% 
  left_join(lrp_gcc_df[c("objectid","pct_hardcoral_transform")]) %>% 
  rename(pct_hardcoral_obs = pct_hardcoral_transform) %>% 
  # add predicted 'brightspots'
  mutate(cc_pred_qt75 = if_else(pct_hardcoral_predicted >= cc_pred_qt[4], 1, 0))

#allreefs_cc %>% head
  
# transform predictions to spatial data
allreefs_cc_sf <- allreefs_cc %>% 
  st_as_sf()

# check CRS is '4326' (OK)
st_crs(allreefs_cc_sf)

```

## Save predictions
```{r}
write_rds(allreefs_cc, here("outputs","allreefs_pred_cc.RDS"))

write_rds(allreefs_cc_sf, here("outputs","allreefs_pred_cc_sf.RDS"))

# SAVE as GEOJSON ----
fn <- here("outputs",
           "allreefs_pred_cc.geojson")

if(file.exists(fn)){file.remove(fn)}

allreefs_cc_sf %>% 
  st_write(dsn = fn, layer = "all_reefs_pred_cc")

```

# Predict Counterfactual (grids)
If there were NO management (in KNOWN management areas, (n = 8190 cells where 
management is "restricted" or "no take")), what would predicted coral cover be? 
- Restricted & No-take become OPEN ACCESS
-- n = 8190 cells (about 15% of the data has partial/full restriction)
-- Option: Use only cells where some management is taking place (n = 8190); 
- Current: Making predictions for all possible cells with complete data (n = 54298), same as baseline prediction. Can subset later as needed.



```{r}
counterfac_df <- predict_df %>% 
  # make all restricted or no-take areas == "open access" to represent the counterfactual
  mutate(mgmt_highest_orig = mgmt_highest) %>% 
  mutate(mgmt_highest = "open access", 
         mgmt_highest = factor(mgmt_highest, levels = c("no take", "restricted", "open access")))

counterfac_df %>% select(-geometry) %>% skim()

counterfac_predict <- predict.gam(gcc_mdl, type = "response",
                                  newdata=counterfac_df, se.fit = T)

counterfac_df$pct_hardcoral_counterfac <- counterfac_predict[[1]]
counterfac_df$pct_hardcoral_counterfac_se <- counterfac_predict[[2]]

counterfac_df %>% filter(!is.na(pct_hardcoral_counterfac)) %>% nrow() # 54298

counterfac_df %>% 
  filter(mgmt_highest_orig %in% c("restricted","no take")) %>% 
  filter(!is.na(pct_hardcoral_counterfac)) %>% 
  nrow() # 8166

```

## Transform & save predictions
```{r}

# spatial transform
counterfac_sf <- counterfac_df %>% 
  st_as_sf()

# check CRS is '4326' (OK)
st_crs(counterfac_sf)

# save predictions ---

write_rds(counterfac_df, here("outputs","allreefs_counterfac.RDS"))

write_rds(counterfac_sf, here("outputs","allreefs_counterfac_sf.RDS"))

# SAVE as GEOJSON ----
fn <- here("outputs",
           "allreefs_counterfac.geojson")

if(file.exists(fn)){file.remove(fn)}

counterfac_sf %>% 
  st_write(dsn = fn, layer = "allreefs_counterfac")


```

# Predict counterfactual - partial and full restrictions
What happens to global (or regional) coral cover means with x,y,z % increase in partial or full restrictions?

NOT IN USE

```{r}
vals <- c(0.10, 0.20, 0.30, 0.40, 0.50, 0.0)
n_cells <- 54596


# simplified: 
s2_increased_mgmt <- 
  data.frame(pr_restricted = c(vals, rep(0,5)),
              pr_closed = c(rep(0,5),vals)) %>% 
  as_tibble() %>% 
  mutate(n_restricted = n_cells*pr_restricted, 
         n_closed = n_cells*pr_closed) %>% 
  mutate(cc_predicted = NA)

for(i in 1:nrow(s2_increased_mgmt)){
  cat("processing scenario",i,"...\n")
  # open --> restricted
  mgmt <- predict_df$mgmt_highest
  open_access <- which(mgmt == "open access")
  n_sample_r <- s2_increased_mgmt$n_restricted[i]
  index_vals_r <- sample(open_access, n_sample_r, replace = F)
  mgmt[index_vals_r] <- "restricted"
  
  # open --> closed
  open_access2 <- which(mgmt == "open access")
  n_sample_c <- s2_increased_mgmt$n_closed[i]
  index_vals_c <- sample(open_access2, n_sample_c, replace = F)
  mgmt[index_vals_c] <- "no take"
  
  
  scenario_df <- predict_df %>%
    mutate(mgmt_highest = mgmt)
  
  # Takes ~1min
  scenario_predict <- predict.gam(gcc_mdl, type = "response", 
                                  newdata=scenario_df, se.fit = F)
  
  s2_increased_mgmt$cc_predicted[i] <- scenario_predict %>% median(na.rm=T)
}

s2_increased_mgmt

# plot results
s2_increased_mgmt %>% 
  pivot_longer(c(pr_restricted,pr_closed), names_to = "condition", values_to = "pr_change") %>%
  filter(pr_change != 0) %>% 
  ggplot(aes(x = pr_change, ymin = 0, ymax = cc_predicted, colour = condition, 
             fill = condition))+
  geom_ribbon(alpha = 0.6)

```




# Predict counterfactual (SITES)
- Make counterfactual predictions for site-level data 
  (for all site types: no-take, restricted, open-access)
- NOTE: site level predictions are based on 5km resolution environmental (etc) data

```{r}
cc_allreefs

counterfac_sites_df <- cc_allreefs %>% 
  as_tibble() %>% 
  select(site, country, latitude, longitude, pct_hardcoral, all_of(gcc_vars)) %>% 
  mutate(pct_hardcoral = pct_hardcoral/100) %>% 
  mutate(mgmt_highest_orig = mgmt_highest) %>% 
  # make all restricted or no-take areas == "open access" to represent the counterfactual
  mutate(mgmt_highest = "open access", 
         mgmt_highest = factor(mgmt_highest, 
                               levels = c("no take", "restricted", "open access")))

# Checks
counterfac_sites_df %>% tabyl(mgmt_highest)
counterfac_sites_df %>% tabyl(mgmt_highest_orig) # should have ALL open access sites

counterfac_sites_df%>% skim()

counterfac_sites_predict <- predict.gam(gcc_mdl, 
                                        type = "response",
                                        newdata=counterfac_sites_df, 
                                        se.fit = T)

counterfac_sites_df$pct_hardcoral_counterfac <- counterfac_sites_predict[[1]]
counterfac_sites_df$pct_hardcoral_counterfac_se <- counterfac_sites_predict[[2]]


# save predictions
write_rds(counterfac_sites_df, here("outputs","counterfac_sites_df.RDS"))


```


