---
title: "03-gcc-v1-4-plots.Rmd"
author: "Whitney Friedman"
date: '2024-05-01'
output: html_document
---

# Plots for gcc v1.4 

```{r setup}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
## Load libraries
```{r}
library(here)
source(here("00-load-cc-libraries.R"))
library(mgcv)
library(sf)
library(RColorBrewer)
library(ggpubr) #plots
library(skimr)
library(kableExtra)

# Mapping
library(leaflet)
library(leaflet.esri)
library(htmlwidgets)
# leaflet provider tile options: 
# https://leaflet-extras.github.io/leaflet-providers/preview/index.html

# GAM plots
library(mgcViz)

```


## Load model
```{r}
gcc_mdl <- read_rds(here("outputs","gcc_v1_4_gam.RDS"))

gcc_mdl_df <- read_rds(here("outputs","gcc_v1_4_gam_df.RDS")) %>% 
  mutate(cc_pred = pct_hardcoral_predicted,
         cc_obs = pct_hardcoral_transform, 
         cc_delta = abs(cc_pred - cc_obs))

gcc_vars <- read_csv(here("intermediate-files","gam_vars_final.csv")) %>% 
  pull(variable)

gcc_vars

```

## Load full allreefs + gcc dataset (55,000 cells) + surveys
```{r}
allreefs_gcc <- read_rds(here("data",
                              "allreefs_gcc.RDS"))
allreefs_gcc

allreefs_gcc_sf <- read_rds(here("data",
                              "allreefs_gcc_sf.RDS"))
allreefs_gcc_sf

# surveys
cc_surveys_sf <- read_rds(here("data",
                              "cc_surveys_combn.RDS")) %>% 
  st_as_sf(coords = c("longitude","latitude"), crs = 4326)

cc_surveys_sf
```



## Load predictions
```{r}
# Baseline prediction
allreefs_pred <- read_rds(here("outputs","allreefs_pred_cc.RDS"))
allreefs_pred %>% select(-geometry) %>% skim()

# Counterfactual predictions - 5km cells
allreefs_counterfac <- read_rds(here("outputs","allreefs_counterfac.RDS"))

allreefs_counterfac %>% select(-geometry) %>% skim()

predict_df <- allreefs_pred %>% 
  left_join(allreefs_counterfac %>% select(objectid, 
                                           pct_hardcoral_counterfac,
                                           pct_hardcoral_counterfac_se))

predict_df %>% select(-geometry) %>% skim()
predict_df %>% names()

# make it a spatial object
predict_sf <- predict_df %>% 
  st_as_sf(crs = 4326)

# Counterfactual predictions - sites
counterfac_sites_df <- read_rds(here("outputs","counterfac_sites_df.RDS"))

# Country_ISO table
country_df <- allreefs_gcc %>% 
  select(country, country_iso) %>% distinct() %>% 
  drop_na()

# Site_ID table
site_id <- counterfac_sites_df %>% 
  select(country, site) %>% 
  group_by(country) %>% 
  reframe(site = site, 
          n = seq(1,n())) %>% 
  left_join(country_df) %>% 
  unite(site_id, c(country_iso,n), sep = "_")
            
site_id

counterfac_sites_df <- counterfac_sites_df %>% 
  left_join(site_id, by = c("country","site")) %>% 
  relocate(site_id) %>% 
  mutate(mgmt_highest_orig = factor(mgmt_highest_orig,
         levels = c("no take", "restricted", "open access")))

counterfac_sites_df

counterfac_sites_df %>% tabyl(mgmt_highest_orig)

```

## Load mapping files 
load mapping files common across regions

```{r}
world <- read_sf(here("globalprep","analysis","mapping","map_data","worldbank_hi_res",
             "WB_countries_Admin0_10m.shp"))


# plot(world,max.plot=1)
# st_crs(world)  # 4326; OK

# colors for plotting coral cover 
map_cols <- c('#92032a','#fee08b','#ffffbf',
                      "#7fcdbb","#41b6c4","#1d91c0", "#225ea8","#0c2c84",
                      '#2c054b')

# Load pac centred map (created with "pac-centred-maps.R")
world3 <- read_rds(here("map-data","world_pac_centred.rds"))

```

# PLOTS of obs vs. predicted by country
3 countries; by grid-cell
NOT CURRENTLY IN USE; using regional plots instead (Figure s7)
```{r}
#countries <- gcc_mdl_df$country %>% unique() # all countries (n = 143); would need to do this loop to create #outputs for every ~10 countries

countries <- c("Belize","Fiji","Tanzania") # focal countries

plt_list = list()
for(i in 1:length(countries)){
  c = countries[i]
  
  # Predictions are already there; just look at Fiji more closely
  country_df <- allreefs_pred %>% 
    filter(country == c,
           !is.na(pct_hardcoral_obs)) %>% 
    mutate(cc_pred = pct_hardcoral_predicted*100, 
           cc_pred_se = pct_hardcoral_predicted_se*100,
           cc_pred_max = cc_pred + cc_pred_se, 
           cc_pred_min = cc_pred - cc_pred_se, 
           #cc_delta = cc_delta*100, 
           cc_obs = pct_hardcoral_obs*100)
  
  
  # NOTE 6/17: FIX THIS PLOT so that the line goes from predicted +/- SE 
  # (not including “observed”) value. (Want to include error in lollipop plots).

  country_plt <- country_df %>% 
    select(objectid, cc_obs, cc_pred, cc_pred_max, cc_pred_min) %>%
    pivot_longer(-c(objectid, cc_pred_max, cc_pred_min), names_to = "var") %>% 
    mutate(var = factor(var)) %>% 
    ggplot(aes(x = reorder(objectid, value), y = value, 
               colour = var, shape = var))+
    geom_segment(aes(y = cc_pred_min, yend = cc_pred_max), 
                 color = "purple", lwd = 0.4, alpha = 0.7)+
    geom_point(size = .9)+
    scale_colour_manual(values = c("grey20","purple"), name = "", 
                        labels = c("Observed", "Predicted"))+
    scale_shape_manual(values = c(19, 21), name = "", 
                        labels = c("Observed", "Predicted"))+
    ylim(0,80)+
    ylab("% live hardcoral")+
    ggtitle(c)+
    theme_bw()+
    theme(axis.text.x = element_blank(), 
          axis.title.x = element_blank(),
          panel.grid = element_line(linewidth=.1, color="gray80"))
  
  plot(country_plt)

  plt_list[[i]] <- country_plt
}


png(here("plots","SM_plots",
         "gcc_v1_4_obs_pred_3countries.png"), 
    res = 300, width = 7, height = 6, units = "in")

ggarrange(plotlist = plt_list[1:length(countries)],
          nrow = length(countries), legend = "bottom", common.legend = T, 
          labels = "AUTO")

dev.off()



```

# MAPS of obs vs. predicted values by country

## Maps of observed & predicted values for 3 focal countries (bz, in, tz)
NEW: 
A - Observed values / cells (looks the same)
B - Filled in grids (prediction at current conditions)
C - counterfactual prediction (prediction of “no management” - for cells where mgmt is known)
D - Lollipop plot - 17 SITES (is the observation - no-mgmt prediction) - dropping a “pin” through each site; compare to 5km counterfactual estimate.  COLOR BY: observed management type

MESSAGE: Can use models to look at whether real places / surveys are above/below predictions. 

Focusing on management in 3 countries.

```{r}

countries <- c("Belize","Fiji","Tanzania") # focal countries

bz_bbox <- c(89,86.9,16,18) # belize xmin,xmax,ymin,ymax    xlim(89,87)+ylim(16,18)+
#in_bbox <- c(-94.5,-142,-11,6) # indonesia - full
#in_bbox <- c(-120.9,-125.1,-8.5,-4.1) # indonesia - zoom
fj_bbox <- c(-176.6, -180, -19.3, -16)
tz_bbox <- c(-38,-41.7,-8.7,-4.9) # tanzania 38,-3.5; 43,-11

# 3 maps with counterfac (no management) prediction
map_list = list()
for(i in 1:length(countries)){
  c = countries[i]
  num_cols = 3
  if(c == "Belize"){bbox = bz_bbox}
  if(c == "Fiji"){bbox = fj_bbox} # num_cols = 1
  if(c == "Tanzania"){bbox = tz_bbox}
  
  country_df <- predict_df %>% 
    filter(country == c) %>% 
    mutate(cc_pred = pct_hardcoral_predicted*100, 
           cc_obs = pct_hardcoral_obs*100, 
           cc_counterfac = pct_hardcoral_counterfac*100)

  # convert country data to sf
  country_sf <- country_df %>% 
    pivot_longer(cols = c(cc_obs, cc_pred, cc_counterfac), names_to = "var",
                 values_to = "pct_hardcoral") %>% 
    mutate(var = factor(var, levels = c("cc_obs","cc_pred","cc_counterfac")), 
           var = recode_factor(var, 
                               "cc_obs" = "Observed",
                               "cc_pred" = "Predicted (observed conditions)", 
                               "cc_counterfac" = "Predicted (no mgmt)")) %>% 
    filter(var != "Predicted (no mgmt)") %>% 
    st_as_sf(crs = 4326)

  # observed, predicted-base, predicted-nomgmt
  country_map <- ggplot(country_sf) +
    geom_sf(aes(fill = pct_hardcoral), lwd = 0.1, color = "gray70")+
    scale_fill_gradientn(colours = map_cols, limits = c(0,100), na.value = "gray90",
                         name = "% Live hard coral")+
    geom_sf(data = world, fill = "gray30")+
    xlim(bbox[1],bbox[2])+
    ylim(bbox[3],bbox[4])+
    facet_wrap(~var, ncol = num_cols)+
    ggtitle(c)+
    theme_rotate()+
    theme(legend.position = "right", 
          axis.text.x = element_blank(), 
          axis.text.y = element_blank(),
          strip.background = element_rect(fill = "white", color = "white"),
          strip.text = element_text(color = "black", size = 8, hjust = 0))
  
  map_list[[i]] <- country_map
  print(country_map)
  
}

```

## Site-level predictions vs. observed

```{r}
rm(country_df)
#checks
counterfac_sites_df %>% tabyl(mgmt_highest_orig) %>% adorn_totals()
counterfac_sites_df %>% tabyl(mgmt_highest) %>% adorn_totals()

# focal countries
countries <- c("Belize","Fiji","Tanzania")

site_plots = list()
for(i in 1:length(countries)){
  c = countries[i]

  if(c != "Fiji"){
  country_df <- counterfac_sites_df %>%
    filter(country == c,
           !is.na(pct_hardcoral_counterfac)) %>%
    slice_sample(n = 20, by = "mgmt_highest_orig")}

  # there are: 0 open access sites in Fiji; 30 no-take, 680 'restricted'
  if(c == "Fiji"){
  country_df <- counterfac_sites_df %>% 
    filter(country == c,
           !is.na(pct_hardcoral_counterfac)) %>%
    slice_sample(n = 30, by = "mgmt_highest_orig")}
  
  #cat(c, "\n")
  #country_df %>% tabyl(mgmt_highest_orig) %>% adorn_totals() %>% print()}
  
  country_df_pred <- country_df %>% 
        mutate(cc_obs = pct_hardcoral * 100, 
           cc_pred = pct_hardcoral_counterfac * 100, 
           cc_pred_se = pct_hardcoral_counterfac_se *100,
           cc_pred_max = cc_pred + cc_pred_se, 
           cc_pred_min = cc_pred - cc_pred_se)
  
  site_plt <- country_df_pred %>%
    ggplot(aes(y = reorder(site, cc_obs), x = cc_obs, shape = mgmt_highest_orig))+
    # segment from obs to predicted:
    geom_segment(aes(y = reorder(site, cc_obs), xend = cc_pred), 
                 colour = "gray60", lwd = 0.4)+
    # segment from pred_min to pred_max
    geom_segment(aes(y = reorder(site, cc_obs), x = cc_pred_min, 
                     xend = cc_pred_max), 
                 lwd = 0.5, colour = "black")+
    # add predicted points
    geom_point(aes(y = reorder(site, cc_obs), x = cc_pred), size = 2, color = "black", fill = "black", stroke = 0)+
    # add observed points, colored by % coral 
    geom_point(aes(fill = cc_obs), size = 2, color = "gray50", stroke = 0.2)+
    scale_fill_gradientn(colours = map_cols, limits = c(0,100), na.value = "gray90",
                         name = "% Live hard coral observed")+
    scale_shape_manual(values = c(21, 24, 22))+
    guides(shape = "none")+
    facet_wrap(~mgmt_highest_orig, nrow = 3, scales = "free_y",
               strip.position = "right")+
    xlab("% Live hard coral")+
    xlim(0,85)+
    scale_y_discrete(position = "right")+
    ggtitle(label = "", subtitle = "Impact Assessment")+
    theme_light()+
    theme(panel.grid.major = element_line(linewidth =.1, color="gray90"), 
          axis.text.y = element_text(size = 5), 
          axis.title.y = element_blank(),
          #strip.background = element_rect(fill = "white", color = "white"), 
          legend.position = "bottom")
  plot(site_plt)
  
  site_plots[[i]] <- site_plt
}


```

# Figure 3: Country plots
Combine country plots and save figure
SUPER interesting to see how many sites are BELOW prediction in open access vs. other 2 categories
```{r}
#unit(c(top, right, bottom, left), units).

plt_combined <- ggarrange(
 # Belize
  ggarrange(
    map_list[[1]]+
      theme(plot.margin = unit(c(.5,0,1,-6), 'lines'),
                                legend.position = "none"),
    site_plots[[1]]+
      scale_y_discrete(position = "right")+
      xlab("")+
      theme(plot.margin = unit(c(-.5,4,-.5,-8), 'lines'), 
            legend.position = "none"), 
    nrow = 1, widths = c(3.5,1), labels = c("A","")),
  # Fiji
  ggarrange(
    map_list[[2]]+
      theme(plot.margin = unit(c(.5,0,1,-6), 'lines'),
                        legend.position = "none"),
    site_plots[[2]]+
      xlab("")+
      scale_y_discrete(position = "right")+
      theme(plot.margin = unit(c(-.5, 2,-.5,-8), 'lines'),
            legend.position = "none"), 
  nrow = 1, widths = c(3.5,1), labels = c("B","")),
  # Tanzania
  ggarrange(
    map_list[[3]]+
      theme(plot.margin = unit(c(.5,0,1,-6), 'lines'),
            legend.position = "bottom"),
    site_plots[[3]]+
      xlab("")+
      scale_y_discrete(position = "right")+
      theme(plot.margin = unit(c(-.5,2.5,3,-8), 'lines'),
            legend.position = "none"),
    nrow = 1, widths = c(3.5,1), labels = c("C","")),
  # all plots
  nrow = 3, heights = c(1,1,1.2), common.legend = T, legend = "bottom")

ggsave(here("plots",
          "gcc_v1_4_obs_pred_3countries_counterfac.png"), plot = plt_combined, 
     width = 11, height = 12, bg = "white")
```



# Figure 1 v1: Surveys and coral grids 
Figure 1 in MS
PACIFIC CENTERED!
Matches Figure 4

```{r}

# Takes ~10min to generate buffers
# doesn't help.
#coral_cells_buffered <- allreefs_gcc_sf %>% 
#  select(objectid:longitude) %>% 
#  st_buffer(., dist = 2) # dist is the buffer distance

# Global map of coral grids and survey points
survey_map <- ggplot(world3)+
  # world
  # geom_sf(fill = "gray95", color = "gray95", lwd = 0.01)+ # light
  geom_sf(fill = "gray20", color = "gray20", lwd = 0.01)+ # dark
  # coral grids
  geom_sf(data = predict_sf, aes(fill = region, color = region), 
          lwd = 0)+ #, color = "transparent")+
  # surveys
    geom_sf(data = cc_surveys_sf, size = 1.5, alpha = .8, shape = 4, stroke = 0.1,
            color = "gray90")+ # light: grey10, dark: grey70; shape = 1 or 4
    xlim(-140,165)+
    ylim(-50,50)+
    coord_sf(expand = F)+
    theme_bw()+
    theme(legend.position = "none", 
          panel.background = element_rect(fill = "gray50"), # light: gray85
          axis.text = element_text(size = 8, color = "black"),
          panel.grid = element_blank())

#survey_map

ggsave(here("plots",
          "survey_map.png"),plot = survey_map, height = 4, width = 9, dpi = 600)
  

```

# Figure 1 v2: Surveys and coral grids 
Figure 1 in MS
PACIFIC CENTERED!
Light version

```{r}

# Takes ~10min to generate buffers
# doesn't help.
#coral_cells_buffered <- allreefs_gcc_sf %>% 
#  select(objectid:longitude) %>% 
#  st_buffer(., dist = 2) # dist is the buffer distance

# Global map of coral grids and survey points
survey_map <- ggplot(world3)+
  # world
  geom_sf(fill = "gray60", color = "gray60", lwd = 0.01)+ # light
  # coral grids
  geom_sf(data = predict_sf, aes(fill = region, color = region), 
          lwd = 0)+ #, color = "transparent")+
  # surveys
    geom_sf(data = cc_surveys_sf, size = 1, alpha = 0.6, shape = 16, stroke = 0.1,
            color = "gray20")+ # light: grey10, dark: grey70; shape = 1 or 4
    xlim(-140,165)+
    ylim(-45,45)+
    coord_sf(expand = F)+
    theme_bw()+
    theme(legend.position = "none", 
          panel.background = element_rect(fill = "gray90"), # light: gray85
          axis.text = element_text(size = 8, color = "black"),
          panel.grid = element_blank())

#survey_map

ggsave(here("plots",
          "survey_map_v2.png"), plot = survey_map, height = 3, width = 8, dpi = 600)
  

```

# Figure 4 v1: Map of observed and predicted coral cover (baseline)
Matches Fig 1 V1

```{r}
na_fill = "gray65" 
#na_fill = "black"

# Global map of OBSERVED coral cover (filled)
global_observed <- ggplot(world3)+
 #world
  geom_sf(fill = "gray20", color = "gray20", lwd = 0.01)+
# predicted 
  geom_sf(data = predict_sf, aes(fill = pct_hardcoral_obs*100), 
            lwd = 0.01, color = "transparent")+
    scale_fill_gradientn(colours = map_cols, limits = c(0,100), na.value = na_fill,
                         name = "% Live hardcoral")+
    xlim(-140,165)+
    ylim(-40,40)+
    coord_sf(expand = F)+
    theme_bw()+
    theme(legend.position = "none", 
          panel.background = element_rect(fill = "gray50"),
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          panel.grid = element_blank())

#global_observed

global_predicted <- ggplot(world3)+
  geom_sf(fill = "gray20", color = "gray20", lwd = 0.01)+
  geom_sf(data = predict_sf, aes(fill = pct_hardcoral_predicted*100), 
            lwd = 0.01, color = "transparent")+
    scale_fill_gradientn(colours = map_cols, limits = c(0,100), na.value = na_fill,
                         name = "% Live hardcoral")+
    xlim(-140,165)+
    ylim(-40,40)+
    coord_sf(expand = F)+
    theme_bw()+
    theme(legend.position = "none", 
          panel.background = element_rect(fill = "grey50"),
          axis.ticks = element_blank(),
          axis.text = element_blank(),
          panel.grid = element_blank())


global_obs_pred <- ggarrange(global_observed, global_predicted, 
                             nrow = 2, labels = "AUTO",
                             font.label = list(color = "black"))

ggsave(here("plots", 
            "global_obs_pred_map.png"),plot = global_obs_pred, 
       bg = "white", height = 4.5, width = 8.5, dpi = 600)

```

# Figure S7: Regional distributions of predicted %CC
- Distributions of the baseline* predictions by region. 
- Supplemental table providing the prediction range, median and 95% CI for each country as well.

Use: gridded predictions for all three management categories

```{r}

predict_df %>% names()
predict_df %>% tabyl(region)
predict_df$pct_hardcoral_obs %>% max(na.rm=T)
predict_df$pct_hardcoral_obs %>% min(na.rm=T)
predict_df$pct_hardcoral_predicted %>% max(na.rm=T)
predict_df$pct_hardcoral_predicted %>% min(na.rm=T)
predict_df %>% 
  group_by(region) %>% 
  reframe(max_obs = max(pct_hardcoral_obs, na.rm=T))

predict_df %>% 
  ggplot(aes(x = objectid, y = pct_hardcoral_obs))


regions <- sort(unique(predict_df$region) %>% as.character())

plt_list = list()
for(i in 1:length(regions)){
  r = regions[i]
  
  # Predictions are already there; just look at Fiji more closely
  region_df <- allreefs_pred %>% 
    filter(region == r,
           !is.na(pct_hardcoral_obs)) %>% 
    mutate(cc_pred = pct_hardcoral_predicted*100, 
           cc_pred_se = pct_hardcoral_predicted_se*100,
           cc_pred_max = cc_pred + cc_pred_se, 
           cc_pred_min = cc_pred - cc_pred_se, 
           #cc_delta = cc_delta*100, 
           cc_obs = pct_hardcoral_obs*100)
  
  ymax = max(region_df$cc_obs, na.rm=T)+5
  
  
  # NOTE 6/17: FIX THIS PLOT so that the line goes from predicted +/- SE 
  # (not including “observed”) value. (Want to include error in lollipop plots).

  region_plt <- region_df %>% 
    select(objectid, cc_obs, cc_pred, cc_pred_max, cc_pred_min) %>%
    pivot_longer(-c(objectid, cc_pred_max, cc_pred_min), names_to = "var") %>% 
    mutate(var = factor(var)) %>% 
    left_join(region_df %>% select(objectid, cc_obs)) %>% 
    ggplot(aes(x = reorder(objectid, cc_obs), y = value, 
               colour = var, shape = var, linetype = "SE"))+
    geom_segment(aes(y = cc_pred_min, yend = cc_pred_max), 
                 color = "purple", lwd = 0.4, alpha = 0.7)+
    geom_point(size = .9)+
    scale_colour_manual(values = c("grey20","purple"), name = "", 
                        labels = c("Observed", "Predicted"))+
    scale_shape_manual(values = c(19, 21), name = "", 
                        labels = c("Observed", "Predicted"))+
    scale_linetype_manual(values = c(1), name = "")+
    ylim(0,ymax)+
    ylab("% live hardcoral")+
    ggtitle(r)+
    theme_bw()+
    ylab("")+xlab("")+
    theme(axis.text.x = element_blank(), 
          axis.title.x = element_blank(),
          panel.grid = element_line(linewidth=.1, color="gray80"))
  
  plot(region_plt)

  plt_list[[i]] <- region_plt
}


png(here("plots","SM_plots",
         "gcc_v1_4_obs_pred_regions.png"), 
    res = 600, width = 10, height = 13, units = "in")

# side by side: width = 17, height = 9
#ggarrange(plt_list[4][[1]],plt_list[9][[1]],
#          plt_list[3][[1]],plt_list[11][[1]],
#          plt_list[2][[1]],plt_list[8][[1]],
#          plt_list[6][[1]],plt_list[5][[1]],
#          plt_list[1][[1]],plt_list[10][[1]],
#          plt_list[7][[1]],
#          nrow = 6, ncol = 2, widths = c(1.2,1),
#          legend = "bottom", common.legend = T, labels = "AUTO")

ggarrange(plotlist = plt_list[1:length(regions)],
          nrow = length(regions), legend = "bottom", common.legend = T, 
          labels = "AUTO")

dev.off()
         

```


# Figure S8: Regional summary of predicted %CC
Of predicted coral cover under current conditions

```{r}

z_value <- qnorm(0.975)  # 95% confidence interval

table_s6 <- predict_df %>% 
  group_by(region) %>% 
  reframe(cc_obs_median = median(pct_hardcoral_obs, na.rm=T),
          cc_pred_median = median(pct_hardcoral_predicted, na.rm=T),
          cc_pred_se_median = median(pct_hardcoral_predicted_se, na.rm=T),
          cc_pred_ci_lower =  cc_pred_median - z_value * cc_pred_se_median, 
          cc_pred_ci_upper = cc_pred_median + z_value * cc_pred_se_median, 
          cc_pred_delta = abs(cc_pred_median - cc_obs_median)) %>% 
  mutate(across(cc_obs_median:cc_pred_delta, ~ . * 100))

table_s6
  

table_s6 %>% 
  mutate(delta = cc_obs_median-cc_pred_median, 
         better_worse = if_else(delta > 0, "Obs > Pred", "Pred > Obs")) %>% 
  mutate(region = factor(region, levels = rev(levels(table_s6$region)))) %>% 
  ggplot(aes(x = cc_obs_median, y = reorder(region,cc_obs_median)))+
  geom_segment(aes(x = cc_pred_ci_lower, xend = cc_pred_ci_upper), 
               color = "purple", lwd = 1)+
  geom_point(aes(x = cc_pred_median), color = "purple", shape = 1, size = 3)+
  geom_point(size = 3)+ 
  geom_vline(xintercept = 30, lty = 2, color = "grey30")+
  xlab("% Live hard coral")+ylab("")+
  xlim(0,60)+
  theme_bw()
  #facet_wrap(~better_worse, ncol = 1, scales = "free_y")

  
ggsave(here("plots","SM_plots",
         "FigS8_Regional_prediction_summary.png"), 
       height = 5, width = 9)

```
# Paper stats
```{r}
predict_df %>% select(-geometry) %>% 
  skim()

sum(!is.na(predict_df$pct_hardcoral_predicted)) # number of cells with s0 predictions
sum(!is.na(predict_df$pct_hardcoral_counterfac)) # number of cells with s1 predictions (8166)

# number of cells per management category
gcc_mdl_df %>% 
  tabyl(mgmt_highest)

gcc_mdl_df %>% 
  tabyl(method_cat) 

# number of countries, regions
```

## Table S7: site-level counterfactual predictions
Used for supplementary table (Table S6)
% of sites that fall above and below by focal country & management classification.
by more than 2x global mean/median SE (~5%)
```{r}
# RESULTS
counterfac_sites_df$pct_hardcoral_counterfac_se %>% mean(na.rm=T)
counterfac_sites_df$pct_hardcoral_counterfac_se %>% median(na.rm=T)

se2 <- counterfac_sites_df$pct_hardcoral_counterfac_se %>% mean(na.rm=T) *2

conterfac_summary <- counterfac_sites_df %>% 
  filter(country %in% c("Belize", "Fiji", "Tanzania")) %>% 
  mutate(obs_v_pred = pct_hardcoral - pct_hardcoral_counterfac,
         above_below_pred = case_when(obs_v_pred > se2 ~ "above", 
                                      obs_v_pred < -1*se2 ~ "below", 
                                      TRUE ~ "neither"))

# Checks
conterfac_summary %>% tabyl(above_below_pred)

conterfac_summary %>% filter(above_below_pred == "above") %>% 
  pull(obs_v_pred) %>% min()

conterfac_summary %>% filter(above_below_pred == "below") %>% 
  pull(obs_v_pred) %>% max()

# table; temp
conterfac_summary %>% tabyl(above_below_pred, country) %>% adorn_totals()

# N sites above/below predicted by country & management cat
conterfac_summary_total_sites <- conterfac_summary %>% 
  group_by(country, mgmt_highest_orig) %>% 
  reframe(total_sites = n())

# final 
conterfac_summary %>% 
  group_by(country, above_below_pred, mgmt_highest_orig) %>% 
  reframe(n_sites = n(), 
            observed_mean = mean(pct_hardcoral, na.rm=T), 
            predicted_mean = mean(pct_hardcoral_counterfac, na.rm=T)) %>% 
  left_join(conterfac_summary_total_sites, by = c("country","mgmt_highest_orig")) %>% 
  mutate(pct_total = n_sites/total_sites) %>% 
  select(country, above_below_pred, mgmt_highest_orig,
         n_sites,total_sites, pct_total, 
         observed_mean, predicted_mean) %>% 
  arrange(country, mgmt_highest_orig, above_below_pred) %>% 
  view()

# N sites above/below predicted by country only
conterfac_summary_total_sites_c <- conterfac_summary %>% 
  group_by(country) %>% 
  reframe(total_sites = n())

# final 
conterfac_summary %>% 
  group_by(country, above_below_pred) %>% 
  reframe(n_sites = n(), 
            observed_mean = mean(pct_hardcoral, na.rm=T), 
            predicted_mean = mean(pct_hardcoral_counterfac, na.rm=T)) %>% 
  left_join(conterfac_summary_total_sites_c, by = "country") %>% 
  mutate(pct_total = n_sites/total_sites) %>% 
  select(country, above_below_pred,
         n_sites,total_sites, pct_total, 
         predicted_mean, observed_mean) %>% 
  arrange(country, above_below_pred) %>% 
  view()

```


