---
title: "05-global-maps.Rmd"
author: "Whitney Friedman"
output: html_document
---

# 05-global-maps
Create global maps of gcc predictions 
using the GAM model (gcc_v1.4) developed in 04a-gc-v1-4-model.Rmd

This script produces an html / leaflet map that can be viewed using a browser.

# Setup
```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```

## load libraries & functions
```{r message=FALSE, warning=FALSE, include=FALSE}
library(here)
source(here("00-load-cc-libraries.R"))
library(mgcv)
library(sf)
library(RColorBrewer)
library(leaflet)
library(leaflet.esri)
library(htmlwidgets)
# leaflet background tiles:
# https://leaflet-extras.github.io/leaflet-providers/preview/index.html
```

## load allreefs predictions
predicted coral cover for allreefs grid
generated in 05-predict-allreefs.Rmd

```{r}
# Baseline prediction
allreefs_pred <- read_rds(here("outputs","allreefs_pred_cc.RDS"))
allreefs_pred %>% select(-geometry) %>% skim()

# Counterfactual predictions - 5km cells
allreefs_counterfac <- read_rds(here("outputs","allreefs_counterfac.RDS"))

allreefs_counterfac %>% select(-geometry) %>% skim()

predict_df <- allreefs_pred %>% 
  left_join(allreefs_counterfac %>% select(objectid, pct_hardcoral_counterfac))

predict_df %>% select(-geometry) %>% skim()

predict_sf <- predict_df %>% 
  st_as_sf()

predict_sf

```

# Maps

## allreefs predictions
- make a global map we can zoom into.
- predicted %cc and observed %cc
```{r}

predict_sf2 <- predict_sf %>% 
  mutate(pct_hardcoral_obs = pct_hardcoral_obs*100, 
         pct_hardcoral_predicted = pct_hardcoral_predicted*100, 
         pct_hardcoral_counterfac = pct_hardcoral_counterfac*100)
  
# 9 colors; first 3 are red to yellow
pal <- colorNumeric(c('#92032a','#fee08b','#ffffbf',
                      "#7fcdbb","#41b6c4","#1d91c0", "#225ea8","#0c2c84",
                      '#2d0355'), domain = seq(0,100,5))

allreefs_cc_map <- leaflet(predict_sf2,
                     options = leafletOptions(preferCanvas = TRUE)) %>% #faster
  # center map on Indonesia
  setView(126, -5, zoom = 6) %>% 
  # background
  addProviderTiles("CartoDB.DarkMatter", options = providerTileOptions(
    updateWhenZooming = FALSE,       # map won't update tiles until zoom is done
    updateWhenIdle    = FALSE)) %>%     # map won't load new tiles when panning
  # % cc observed 
  addPolygons(
    color = "gray30", weight = .5, fillOpacity = 1,
    fillColor = ~pal(pct_hardcoral_obs),
    popup = paste(paste("Region:", predict_sf2$region),
                  paste("Country:", predict_sf2$country),
                  paste("Management:", predict_sf2$mgmt_highest),
                  paste("%CC Obs:", round(predict_sf2$pct_hardcoral_obs, 3)),
                  paste("%CC Pred:", round(predict_sf2$pct_hardcoral_predicted, 3)),
                  sep = "<br/>"),    
    group = "pct_hardcoral_obs") %>%
  # % cc predicted (current conditions)
  addPolygons(
    color = "gray30", weight = .5, fillOpacity = 1,
    fillColor = ~pal(pct_hardcoral_predicted),
    popup = paste(paste("Region:", predict_sf2$region),
                  paste("Country:", predict_sf2$country),
                  paste("Management:", predict_sf2$mgmt_highest),
                  paste("%CC Obs:", round(predict_sf2$pct_hardcoral_obs, 3)),
                  paste("%CC Pred:", round(predict_sf2$pct_hardcoral_predicted, 3)),
                  sep = "<br/>"),
    group = "pct_hardcoral_s0_current") %>% 
  # % cc predicted (counterfactual)
    addPolygons(
    color = "gray30", weight = .5, fillOpacity = 1,
    fillColor = ~pal(pct_hardcoral_counterfac),
    popup = paste(paste("Region:", predict_sf2$region),
                  paste("Country:", predict_sf2$country),
                  paste("Management:", predict_sf2$mgmt_highest),
                  paste("%CC Obs:", round(predict_sf2$pct_hardcoral_obs, 3)),
                  paste("%CC Pred (counterfac):", round(predict_sf2$pct_hardcoral_counterfac, 3)),
                  sep = "<br/>"),
    group = "pct_hardcoral_s1_no_mgmt") %>% 
  # add legend
  addLegend("bottomright", pal = pal, values = ~seq(0,100,5),
    title = "% Live hard coral",
    opacity = 1) %>%   
  # add Layer controls
  addLayersControl(overlayGroups=c("pct_hardcoral_obs",
                                   "pct_hardcoral_s0_current",
                                   "pct_hardcoral_s1_no_mgmt"),
                 options=layersControlOptions(collapsed=F))

# Save map (this takes awhile)
saveWidget(allreefs_cc_map, file = here("maps", "gcc_v1_4_allreefs.html"),
           title = "gcc_v1_4_allreefs")
```

